---
output: github_document
---


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
``` 

# Replication: The Effect of Mandatory COVID-19 Certificates on Vaccine Uptake

This repository provides all materials for replication of results in

> Mills, M. C., and Rüttenauer, T. (2021). The Effect of Mandatory COVID-19 Certificates on Vaccine Uptake: Synthetic-Control Modelling of Six Countries. *The Lancet Public Health*, OnlineFirst. https://doi.org/10.1016/S2468-2667(21)00273-5

Date: 2021-12-23 


## Set up

The code for replication of the results requires the following folders: “01\_Script”, “02\_Data”, “03\_Output”. All R Scripts are required in folder “01\_Script”, all data are required in folder “02\_Data”.

To reproduce the results of the paper, the scripts need to be executed in order.

The following packages are necessary for reproduction of main results:

```{r pkgs, eval = FALSE} 
install.packages(Synth)
install.packages(SCtools)
install.packages(ggplot2)
install.packages(viridis)
install.packages(cowplot)
install.packages(texreg)
install.packages(grid)
install.packages(gridtext)
install.packages(gridExtra)
install.packages(colorspace)
install.packages(parallel)
install.packages(doParallel)
install.packages(future.apply)
install.packages(ISOweek)
install.packages(WDI)
install.packages(wpp2019)
```

### Scripts: 

- *01_Download_Data*: Downloads and prepares data from Our World in Data and OxCGRT.

- *02_Synthetic_Control_bootstrap*: Performs the main synthetic control analysis.

- *02b_Synthetic_Control_placebo*: Performs the placebo analysis (appendix).

- *02c_Synthetic_Control_resample*: Performs the resample analysis (appendix).

- *03_Decriptive_age*: Performs age specific analyses from country specific data (in 02_Data).


## Data:

All data for this paper are freely available and accessible online. The sources are documented in the code.

## System and version information

Platform: x86_64-pc-linux-gnu

Version: R version 4.0.5
